---
title: "Nintendo Switch 2 - Flip or Flop"
subtitle: "Leveraging Data Analytics for Strategic Insights on Genre, Platform, and Market Trends"
author: "Group 1"
institute: "GBA 5910, Cal Poly Pomona"
date: '`r format(Sys.time(), "2025,April,7")`'
format: 
  revealjs:
    theme: serif
    width: 1600
    height: 900
    footer: Nintendo Switch 2 - Flip or Flop
    transition: fade
    transition-speed: fast
    incremental: false
    toc: true
    toc-depth: 1
    slide-number: true
    scrollable: true
    smaller: true
    code-fold: false
    code-overflow: wrap
    number-sections: false
    number-depth: 5
    embed-resources: true
editor: visual
execute: 
  echo: true
  freeze: auto
editor_options: 
  chunk_output_type: console
---

# 1. Problem Definition

-   Lack of sufficient market research by game and console developers for new console success.

-   Focus on Nintendo and the strategic importance of the Switch 2.

-   Potential negative impacts of inadequate research (financial, market position), which could lead to a similar negative result as previous consoles.

# 2. Research Objectives

-   RO1: Genre Trends
-   RO2: Platform Performance
-   RO3: ESRB Rating Impact
-   RO4: Console to Game Ratio
-   RO5: Backward Compatibility

# 3. Why Does It Matter?

-   Our research aims to provide actionable insights for game developers and decision-makers, not just academic analysis.

-   Using data analytics, we will examine genre performance, platform comparisons, and the impact of ESRB ratings on sales.

-   Findings will be directly tied to defined variables and used to inform strategic planning for the upcoming Nintendo Switch 2.

# 4. Population & Sampling/Data Collection

> Define the data population:

-   Historical sales data of video games and consoles across various platforms and time periods, as found in Kaggle datasets. 
-   Describe the data types available (game titles, genres, platforms, sales, ESRB, dates).
-   Outline the data acquisition process (downloading).

# 5. Data Wrangling Plan

## Data Wrangling - From Records to Data

> Process of loading data into R (e.g., read_csv()). Initial data exploration (glimpse(), head()).

### Loading "Video Games Sales 2019"

```{python}
# Ensure this code chunk delineates {python} not {r}
# Uncomment the following line if you haven't installed kagglehub
#!pip install kagglehub

import kagglehub

# Download the latest version of the dataset and assign it to a variable.
directory_path = kagglehub.dataset_download("ashaheedq/video-games-sales-2019")
print("Path to dataset files:", directory_path)
```

```{r}
library(reticulate)
library(tidyverse)

# Retrieve the Python variable from reticulate.
videogamesales2019_path <- py$directory_path

# List CSV files in the directory.
videogamesales2019_csv_files <- list.files(videogamesales2019_path, pattern = "\\.csv$", full.names = TRUE)
print(videogamesales2019_csv_files)

# If there's at least one CSV file, read and show the first few rows.
if(length(videogamesales2019_csv_files) > 0) {
  videogamesales2019 <- read_csv(videogamesales2019_csv_files[2]) # manually changed to item 2 for longer CSV
  head(videogamesales2019)
  glimpse(videogamesales2019)
} else {
  message("No CSV files found in the directory.")
}
```


### Loading "Nintendo Games"

```{python}
import kagglehub

# Download the latest version of the Nintendo Games dataset and assign it to a variable.
nintendogames_path = kagglehub.dataset_download("joebeachcapital/nintendo-games")
print("Path to dataset files:", nintendogames_path)
```

```{r}
library(reticulate)
library(tidyverse)

# Retrieve the Python variable from reticulate.
nintendogames_path <- py$nintendogames_path

# List CSV files in the directory.
nintendogames_csv_files <- list.files(nintendogames_path, pattern = "\\.csv$", full.names = TRUE)
print(nintendogames_csv_files)

# If there's at least one CSV file, read and show the first few rows.
if(length(nintendogames_csv_files) > 0) {
  nintendogames <- read_csv(nintendogames_csv_files[1])
  head(nintendogames)
  glimpse(nintendogames)
} else {
  message("No CSV files found in the directory.")
}
```

## Data Wrangling - Tidying the Data

> Ensuring data adheres to tidy principles. Strategies for handling missing values and inconsistencies. Potential for merging datasets.

## Data Wrangling - Transforming the Data (General)

> Overview of transformations needed for analysis (calculations, extractions, recoding).

-   Clean data by deleting records with missing information that is relevant
-   Join tables together using join functions
-   For example, joining video game sales table to console sales table to examine trends over the years between the two

# 6. RO1: Genre Trends

Measures:

-   Variable 1 (DV): Sales

-   Variable 2 (IV): Genre

-   Variable 3 (IV): Platform

-   Variable 4 (IV): Year

Plan for Data Wrangling: Cleaning genre names, grouping data.

Plan for Data Visualization: Bar charts, line charts.

# 7. RO2: Platform Performance

Measures:

-   Variable 1 (DV): Sales

-   Variable 2 (IV): Platform

-   Variable 3 (IV): Year

Plan for Data Wrangling: Standardizing platform names, aggregating sales.

Plan for Data Visualization: Line charts, bar charts (market share).

# 8. RO3: ESRB Rating Impact

Measures:

-   Variable 1 (DV): Sales

-   Variable 2 (IV): ESRB Rating

-   Variable 3 (IV): Genre

-   Variable 4 (IV): Platform

Plan for Data Wrangling: Ensuring consistent ESRB categories (forcats).

Plan for Data Visualization: Box plots, bar charts.

# 9. R04: Console to Game Ratio

Measures:

-   Variable 1 (DV): Ratio (Game Sales / Console Sales)

-   Variable 2 (IV): Console Sales

-   Variable 3 (IV): Game Sales

-   Variable 4 (IV): Platform

-   Variable 5 (IV): Year

Plan for Data Wrangling: Obtaining console sales (if needed), calculating ratio.

Plan for Data Visualization: Line charts.

# 10. RO5: Backward Compatibility

Measures:

-   Variable 1 (Potential DV): Console Sales

-   Variable 2 (Potential DV): Game Sales

-   Variable 3 (Potential DV): Number of New Releases

-   Variable 4 (Potential IV): Presence/Absence of Backward Compatibility

Plan for Data Wrangling: Identifying consoles with/without BC.

Plan for Data Visualization: Line charts, bar charts (comparisons).

# 11. Conclusion

-   Measuring Nintendo's success with new consoles based on video game sales

-   Data imported from Kaggle

-   Visualizations with correlations between console sales, genres, ESRB ratings, and backward compatibility, our main ROs